Sequential algorithms to split and merge ultra-high resolution 3D images

### 2017-07-26 paper.tex
add mwrites scipts, data

\subsection{Slices vs Blocks}

Figure~\ref{fig:slices-vs-blocks} shows the merging time for Slices vs
Blocks, on SSD and HDD. Merging with Blocks takes about twice the time
of Slices, which motivates the need for improved algorithms to merge
blocks. As expected, seek time is mainly responsible for this
difference, although differences in read times are also observed,
perhaps due to a caching effect at the disk or OS level. This behavior is
reproduced in SSD and HDD, which shows that SSDs might not be the only
solution to reduce seek time.  \todo{On figure: check that breakdowns
  add up to total time. Harmonize time formats. Harmonize colors (all
  slices in purple, all blocks in green). If time permits, try
  histogram for breakdown, on same figure than total time.}
\begin{figure}[h]
  \centering
  \includegraphics[width=0.45\columnwidth]{figures/blocks-slices/totalmergetimeSSD1.pdf}
  \hfill
  \includegraphics[width=0.45\columnwidth]{figures/blocks-slices/totalmergetimeHDD1.pdf}\\
  \includegraphics[width=0.45\columnwidth]{figures/blocks-slices/hddBreakDown1.pdf}
  \hfill
  \includegraphics[width=0.45\columnwidth]{figures/blocks-slices/ssdBreakDown1.pdf}
  \caption{Merging time for Slices and Blocks. Left column: SSD. Right column: HDD. Top row: overall merging time. Bottom row: breakdown by read, write and seek time.}
  % Gnuplot file: scripts/blocks-slices/createboxplot.gnplt
\label{fig:slices-vs-blocks}
\end{figure}

>>>>

\todo{Valerie's results at PERFORM + model.}
% will be used as reference
